NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-29 paper/application.tex
re-arrange figure
add figure

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
%There is no simple answer to what exactly is the information attention captures.
%Can attention capture grammar structure? Is

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 4: Handcraft Example Exploration}
To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference. 
%
%The exploration is just started once the prediction result is examined, 
Often the researchers have a set of experiments they plan test, from which they likely develop new hypothesis for further experiments.
%
In some way, we can think of such a process as a nature blend of all previously discussed scenarios. However,  instead with specific analysis goal in mind, the domain experts focus on probing around and see if they can find anything interesting or out-of-ordinary behaviors in the model.
%
Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and tedious grunt work, allow them to focus on more productive activity.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 4: Explore Relationship Between Grammar and Attention}
There is no simple answer to what exactly is the information attention captures.
Can attention capture grammar structure? Is

\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{depTreeExample}
 \caption{
Dependency tree.
 }
\label{fig:depTreeExample}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcraft Example Exploration}
To test the limitation of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most model will have a difficult time making correct inference.
%
%The exploration is just started once the prediction result is examined,
Often the researchers have a set of experiments they plan test, from which they likely develop new hypothesis for further experiments.
%
In some way, we can think of such a process as a nature blend of all previously discussed scenarios. However,  instead with specific analysis goal in mind, the domain experts focus on probing around and see if they can find anything interesting or out-of-ordinary behaviors in the model.
%
Having an environment, in which the experts can freely modify the words or attention then observe the corresponding changes in other parts of the model pipeline, ensures an streamlined exploration experience that free the users from interruption and tedious grunt work, allow them to focus on more productive activity.
